### 2022-09-27 Thesis/text/implementierung.tex
modification to line spacing, changed bt pictures

The system architecture, depicted in figure \ref{fig:component_diagram}, integrates the behavior tree into the existing architecture. The already existing components are colored in gray, and the newly added components are colored in blue. The new components and their functions are described in the following sections of this chapter.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.9\textwidth]{images/component_diagram_bt.png}
	\caption{Component Diagram of System Architecture}
	\label{fig:component_diagram}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.9\textwidth]{images/simplified_bt.png}
	\caption{Top Level Behavior Tree Structure}
	\label{fig:top_level_bt}
\end{figure}

@@

The design pattern of the system supervisor is an "Watchdog" pattern. This pattern is depicted in figure \ref{fig:watchdog_pattern}. The pattern is used to monitor a system from the outside and directly take corrective measures when problems are detected.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.9\textwidth]{images/sensor_fallback.png}
	\caption{Lidar Fallback}
	\label{fig:lidar_fallback}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.9\textwidth]{images/collision_fallback.png}
	\caption{Collision Fallback Behavior}
	\label{fig:collision_fallback}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.6\textwidth]{images/battery_fallback.png}
	\caption{Battery Fallback Behavior}
	\label{fig:battery_fallback}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.6\textwidth]{images/global_planning_fallback.png}
	\caption{Path Planning Fallback Behavior}
	\label{fig:global_planning_fallback}
\end{figure}

@@

\begin{table}[ht]
	\centering
	\caption{Implemented Custom Services}
	\label{tab:custom_interfaces}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.9\textwidth}{!}{%
		\begin{tabular}{ | m{0.2\textwidth} | m{0.33\textwidth}| m{0.33\textwidth} | m{0.2\textwidth} |} 
	 	\hline
	 	\textbf{Name} & \textbf{Request} & \textbf{Response} \\ 
	 	\hline
	 	GetCharge & Empty & float charge, float idle$\_$decrease$\_$per$\_$sec, float drive$\_$decrease$\_$per$\_$sec \\
	 	\hline
	 	GetDistance & Empty & float distance$\_$in$\_$meter\\ 
	 	\hline
	 	GetLastGoal & Empty & geometry$\_$msgs/Pose last$\_$goal$\_$pose \\ 
	 	\hline
	 	GetLastMap & Empty & nav$\_$msgs/OccupancyGrid map \\
	 	\hline
	 	GetTwistArray & Empty & geometry$\_$msgs/Twist[] cmd$\_$vel$\_$array\\
	 	\hline 	
	 	PubCmdVel & geometry$\_$msgs/Twist cmd$\_$vel, float time$\_$in$\_$seconds & bool success \\
	 	\hline
	 	SendUpdatedMap & nav$\_$msgs/OccupancyGrid updated$\_$map & Empty \\
	 	\hline
		\end{tabular}
	}
\end{table}

>>>>

The system architecture, depicted in figure \ref{fig:component_diagram}, integrates the autonomy layer discussed in section \ref{sec:System Solution} into the existing architecture. The already existing components are colored in gray, and the newly added components are colored in blue. The new components and their functions are described in the following sections of this chapter.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.92\textwidth]{images/component_diagram_bt.png}
	\caption{Component Diagram of System Architecture}
	\label{fig:component_diagram}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.95\textwidth]{images/simplified_bt_inverted.png}
	\caption{Top Level Behavior Tree Structure}
	\label{fig:top_level_bt}
\end{figure}

@@

The design pattern of the system supervisor is a "Watchdog" pattern. This pattern is depicted in figure \ref{fig:watchdog_pattern}. The pattern is used to monitor a system from the outside and directly take corrective measures when problems are detected.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.9\textwidth]{images/sensor_fallback_inverted.png}
	\caption{Lidar Fallback}
	\label{fig:lidar_fallback}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.95\textwidth]{images/collision_fallback_inverted.png}
	\caption{Collision Fallback Behavior}
	\label{fig:collision_fallback}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.6\textwidth]{images/battery_fallback_inverted.png}
	\caption{Battery Fallback Behavior}
	\label{fig:battery_fallback}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.6\textwidth]{images/global_planning_fallback_inverted.png}
	\caption{Path Planning Fallback Behavior}
	\label{fig:global_planning_fallback}
\end{figure}

@@

\begin{table}[ht]
	\centering
	\caption{Implemented Custom Services}
	\label{tab:custom_interfaces}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.95\textwidth}{!}{%
		\begin{tabular}{ | m{0.2\textwidth} | m{0.42\textwidth}| m{0.45\textwidth} |} 
	 	\hline
	 	\textbf{Name} & \textbf{Request} & \textbf{Response} \\ 
	 	\hline
	 	GetCharge & Empty & float charge, float idle$\_$decrease$\_$per$\_$sec, float drive$\_$decrease$\_$per$\_$sec \\
	 	\hline
	 	GetDistance & Empty & float distance$\_$in$\_$meter\\ 
	 	\hline
	 	GetLastGoal & Empty & geometry$\_$msgs/Pose last$\_$goal$\_$pose \\ 
	 	\hline
	 	GetLastMap & Empty & nav$\_$msgs/OccupancyGrid map \\
	 	\hline
	 	GetTwistArray & Empty & geometry$\_$msgs/Twist[] cmd$\_$vel$\_$array\\
	 	\hline 	
	 	PubCmdVel & geometry$\_$msgs/Twist cmd$\_$vel, float time$\_$in$\_$seconds & bool success \\
	 	\hline
	 	SendUpdatedMap & nav$\_$msgs/OccupancyGrid updated$\_$map & Empty \\
	 	\hline
		\end{tabular}
	}
\end{table}

### 2022-09-27 Thesis/text/methoden.tex
modification to line spacing, changed bt pictures

\begin{table}[ht]
	\centering
	\caption{ROS Communication Options}
	\label{tab:ros_interfaces}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.9\textwidth}{!}{%
		\begin{tabular}{ | m{0.15\textwidth} | m{0.3\textwidth}| m{0.3\textwidth} | m{0.2\textwidth}|} 
	 	\hline
	 	\textbf{Name} & \textbf{Communication Pattern} & \textbf{Area of Use} & \textbf{Cardinality} \\ 
	 	\hline
	 	Topics & Publisher / Subscriber & Continuous stream of data e.g. sensor data & n:m \\ 
	 	\hline
	 	Services & Request / Response & Get specific data only once & One service, many clients \\ 
	 	\hline
	 	Actions & Request / Response and Publish/ Subscribe & Trigger executing of asynchronous goal-driven processes and receive updates & One action, many clients \\
	 	\hline
		\end{tabular}
	}
\end{table}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.5\textwidth]{images/turtlebot_sim.png}
	\caption{Turtlebot3 model in Gazebo simulator}
	\label{fig:turtlebot}
\end{figure}

@@

\begin{table}[ht]
	\centering
	\caption{Turtlebot3 Specifications}
	\label{tab:turtlebot_spec}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.9\textwidth}{!}{%
		\begin{tabular} {| l | l |} 
			%{| m{0.3\textwidth} | m{0.3\textwidth} |} 
	 	\hline
	 	\textbf{Specification} & \textbf{Value} \\ 
	 	\hline
	 	Maximum translational velocity & 0.26 m/s \\ 
	 	\hline
	 	Maximum rotational velocity & 1.82 rad/s (104.27 deg/s) \\
%	 	\hline
%	 	Maximum payload & 30kg \\
	 	\hline
	 	Size (L x W x H) & 281mm x 306mm x 141mm \\
	 	\hline
	 	Weight & 1.8 kg \\
	 	\hline
	 	Singe Board Computer & Raspberry Pi (3 or 4) \\
	 	\hline
	 	Laser Distance Sensor & 360 Degree Laser Distance Sensor LDS-01 \\
	 	\hline
	 	IMU & Gyroscope 3 Axis, Accelerometer 3 Axis \\
	 	\hline
	 	Actuators & XM430-W210 \\
	 	\hline
		\end{tabular}
	}
\end{table}

@@

\begin{table}[ht]
	\centering
	\caption{Non-Functional Requirements}
	\label{tab:nonfn_req}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.9\textwidth}{!}{%
		\begin{tabular}{ | m{0.13\textwidth} | m{0.13\textwidth}| m{0.1\textwidth} | m{0.55\textwidth} |} 
			\hline
			\textbf{Nr.} & \textbf{Name} & \textbf{Priority} & \textbf{Description} \\ 
			\hline
			non$\_$freq1 & Single Point of Failure & High & The system does not have a single point of failure	When parts of the system fail, the system maintains operability to a degree \\ 
			\hline
			non$\_$freq2 & Performance & High & The system's control loop guarantees fast reactions. The average frequency with which the system checks the sensors/navigation2 is higher than 100Hz (10ms) \\ 
			\hline
			non$\_$freq3 & Determinism & High & The outcome for a given set of inputs must be deterministic, meaning that the behavior is always executed similarly. \\
			\hline
			non$\_$freq4 & Deliberate & High & The robot can execute deliberative behaviors, meaning that behaviors new implemented behaviors go beyond reacting to sensor input and have a planning aspect. \\
			\hline
		\end{tabular}
	}
\end{table}

@@

\section{System Solution}

>>>>

\begin{table}[ht]
	\centering
	\caption{ROS Communication Options}
	\label{tab:ros_interfaces}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.9\textwidth}{!}{%
		\begin{tabular}{ | m{0.12\textwidth} | m{0.37\textwidth}| m{0.3\textwidth} | m{0.139\textwidth}|} 
	 	\hline
	 	\textbf{Name} & \textbf{Communication Pattern} & \textbf{Area of Use} & \textbf{Cardinality} \\ 
	 	\hline
	 	Topics & Publisher / Subscriber & Continuous stream of data e.g. sensor data & n:m \\ 
	 	\hline
	 	Services & Request / Response & Get specific data only once & One service, many clients \\ 
	 	\hline
	 	Actions & Request / Response and Publish / Subscribe & Trigger executing of asynchronous goal-driven processes and receive updates & One action, many clients \\
	 	\hline
		\end{tabular}
	}
\end{table}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.3\textwidth]{images/turtlebot_sim.png}
	\caption{Turtlebot3 model in Gazebo simulator}
	\label{fig:turtlebot}
\end{figure}

@@

\begin{table}[ht]
	\centering
	\caption{Turtlebot3 Specifications}
	\label{tab:turtlebot_spec}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.8\textwidth}{!}{%
		\begin{tabular} {| l | l |} 
			%{| m{0.3\textwidth} | m{0.3\textwidth} |} 
	 	\hline
	 	\textbf{Specification} & \textbf{Value} \\ 
	 	\hline
	 	Maximum translational velocity & 0.26 m/s \\ 
	 	\hline
	 	Maximum rotational velocity & 1.82 rad/s (104.27 deg/s) \\
%	 	\hline
%	 	Maximum payload & 30kg \\
	 	\hline
	 	Size (L x W x H) & 281mm x 306mm x 141mm \\
	 	\hline
	 	Singe Board Computer & Raspberry Pi (3 or 4) \\
	 	\hline
	 	Laser Distance Sensor & 360 Degree Laser Distance Sensor LDS-01 \\
	 	\hline
	 	IMU & Gyroscope 3 Axis, Accelerometer 3 Axis \\
	 	\hline
	 	Actuators & XM430-W210 \\
	 	\hline
		\end{tabular}
	}
\end{table}

@@

\begin{table}[ht]
	\centering
	\caption{Non-Functional Requirements}
	\label{tab:nonfn_req}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.9\textwidth}{!}{%
		\begin{tabular}{ | m{0.11\textwidth} | m{0.14\textwidth}| m{0.1\textwidth} | m{0.7\textwidth} |} 
			\hline
			\textbf{Nr.} & \textbf{Name} & \textbf{Priority} & \textbf{Description} \\ 
			\hline
			non$\_$freq1 & Single Point of Failure & High & The system does not have a single point of failure	When parts of the system fail, the system maintains operability to a degree \\ 
			\hline
			non$\_$freq2 & Performance & High & The system's control loop guarantees fast reactions. The average frequency with which the system operates is higher than 100Hz (10ms) \\ 
			\hline
			non$\_$freq3 & Determinism & High & The outcome for a given set of inputs must be deterministic, meaning that the behavior is always executed similarly. \\
			\hline
			non$\_$freq4 & Deliberate & High & The robot can execute deliberative behaviors, meaning that behaviors new implemented behaviors go beyond reacting to sensor input and have a planning aspect. \\
			\hline
		\end{tabular}
	}
\end{table}

@@

\section{System Solution}
\label{sec:System Solution}
